Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of the Moran process for the Iterated Prisoner's Dilemma

### 2017-10-31 main.tex
Remove a number of references to figures.
This have been moved to the supplementary materials.

When $N=2$ the Moran process is effectively a measure of the distribution of relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. The top 16 (10\%) strategies are
% TODO Fix (have removed plot)
shown in
Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:

@@

\begin{table}[!hbtp]
    \tiny
    \centering
    \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
    \label{tbl:summary_top_2}
    % TODO Explain this more (see comment about error bars)
\end{table}

@@

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).
The ranks of each strategy for all considered values of \(N\) according to mean
\(x_1\) are shown in Figure~\ref{fig:ranks_v_size_invade}.

The fixation
probabilities are shown in
Figures~\ref{fig:boxplot_3_invade},~\ref{fig:boxplot_7_invade}
and~\ref{fig:boxplot_14_invade} for \(N\in\{3, 7, 14\}\) showing the mean
fixation as well as the neutral fixation for each given scenario.

The top 16 strategies are given in Table~\ref{tbl:top_invade}.

@@

In addition to identifying good invaders, strategies resistant to invasion by
other strategies are identified by examining the distribution of $x_{N-1}$ for
each strategy. The ranks of each strategy for all considered values of \(N\)
according to mean \(x_{N-1}\) are shown in
Figures~\ref{fig:ranks_v_size_resist}.

The fixation probabilities are shown in
Figures~\ref{fig:boxplot_3_resist},~\ref{fig:boxplot_7_invade}
and~\ref{fig:boxplot_14_resist} for \(N\in\{3, 7, 14\}\) showing the mean
fixation as well as the neutral fixation for each given scenario.

Table~\ref{tbl:top_resist} shows the top strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
Once again none of the short memory strategies from
Section~\ref{sec:two_individuals} perform well for high \(N\).

@@

To complement Figures~\ref{fig:ranks_v_size_invade}
and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexist} shows
the rank of each strategy based on \(x_{N/2}\).
Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
strategies:

@@

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF3_array.pdf}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_CS_array.pdf}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions). Rows
        correspond to all the strategies considered in this work (ordered
    alphabetically by name).}
    % TODO Add better explanation of repetitions.
    \label{fig:cooperation_rates}
\end{figure}

@@

All source code for this work has been written in a sustainable manner: it is
open source, under version control and tested which ensures that all results can
be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
% TODO Add reference to source code
the processed data has also been properly archived and can be found
at \cite{data}.

@@

\newpage
\bibliographystyle{plain}
\bibliography{tex/bibliography.bib}
% TODO Fix repeated item.

>>>>

When $N=2$ the Moran process is effectively a measure of the distribution of 
relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. The top 16 (10\%) strategies are
shown in
Table~\ref{tbl:summary_top_2} and figures showing the performance of all
strategies are available in the supplementary materials. 
The top five ranking strategies are:

@@

\begin{table}[!hbtp]
    \tiny
    \centering
    \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
    \label{tbl:summary_top_2}
\end{table}

@@

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).

The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
figures showing the performance of all strategies is available in the
supplementary materials.

@@

In addition to identifying good invaders, strategies resistant to invasion by
other strategies are identified by examining the distribution of $x_{N-1}$ for
each strategy.

Table~\ref{tbl:top_resist} shows the top strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
for all strategies are available in the supplementary materials.
Once again none of the short memory strategies from
Section~\ref{sec:two_individuals} perform well for high \(N\).

@@

Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
strategies:

@@

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF3_array.pdf}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_CS_array.pdf}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions). Rows
        correspond to all the strategies considered in this work (ordered
    alphabetically by name).}
    \label{fig:cooperation_rates}
\end{figure}

@@

All source code for this work has been written in a sustainable manner: it is
open source, under version control and tested which ensures that all results can
be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
the processed data has also been properly archived and can be found
at \cite{data}.

@@

\newpage
\bibliographystyle{plain}
\bibliography{tex/bibliography.bib}
